Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-02-22 article.tex
table titles fixed

\begin{table}
	\caption{Test results for experiment 1. HC (Positive) stands for Health Control while P (Negative) means Parkinson's disease.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL04 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL05 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL02 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP04 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP05 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP02 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{\tiny{Mean time-slice accuracy} $\overline{C_{i,t}}$} & 100 &
			\multicolumn{2}{|r|}{\tiny{Mean accuracy} $\overline{C_{i}}$} & 100 \\
			\hline \hline

@@

\begin{table}
	\caption{Test results for experiment 2.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL08 & HC & 191 &  7  & 96.46 & 0.9646 & HC & 100 \\
			CTL12 & HC & 195 &  3  & 98.48 & 0.9848 & HC & 100 \\
			CTL01 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP08 & P   &  1  & 197 & 99.49 & 0.0050 &  P  & 100 \\
			ODP12 & P   &  2  & 196 & 98.99 & 0.0101 &  P  & 100 \\
			ODP01 & P   &  12  & 186 & 93.94 & 0.0606 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.90 &
			\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
			\hline \hline

@@

\begin{table}
\caption{Test results for experiment 3.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL03 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL13 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL14 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		ODP03 & P  &  53  & 145 & 73.23 & 0.2677 &  P  & 100 \\
		ODP13 & P  & 198 &   0   &     0    &      1      & HC  & 0 \\
		ODP14 & P  & 48  &  150 & 75.76  & 0.2424 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 74.83 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 83.33 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 4.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL12 & HC & 185 & 13  & 93.43 & 0.9343 & HC & 100 \\
		CTL06 & HC & 197 &  1   & 99.49 & 0.9949 & HC & 100 \\
		CTL11 & HC & 170 & 28  & 85.86 & 0.8586 & HC & 100 \\
		ODP12 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP11 & P  &   2   & 196 & 98.99 & 0.0101  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 96.30 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100  \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 5.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL15 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		CTL11 & HC & 198  &   0   &  100  & 1 & HC & 100 \\
		CTL07 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		ODP15 & P   &   0   & 198 &  100  & 0 &  P  & 100 \\
		ODP11 & P   &  34  &  164 &82.83& 0.1717 &  P  & 100 \\
		ODP07 & P  &   0   &  198 & 1 00  &0  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.14 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 6.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL10 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL03 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL02 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		ODP10 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP03 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP02 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 100 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 7.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL05 & HC & 194 &  4   & 97.98 & 0.9798 & HC & 100 \\
		CTL04 & HC & 198 &  0   &   100  &      1     & HC & 100 \\
		CTL10 & HC & 186  &  12 & 93.94 & 0.9394 & HC & 100 \\
		ODP05 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP04 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP10 & P  &   0    & 198 &   100  &    0      &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 98.65 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 8.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL09 & HC & 102 & 96  & 51.51 &  0.5151 & HC  & 100 \\
		CTL12 & HC & 122 &  76  & 61.62 & 0.6162 & HC & 100 \\
		CTL06 & HC & 198 &   0  &  100   &    1       & HC & 100 \\
		ODP09 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\
		ODP12 &  P  &   2   & 196 & 98.99 & 0.0101 &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 85.35 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

>>>>

\begin{table}
	\caption{Test results for experiment 1. HC (Positive) stands for Health Control while P (Negative) means Parkinson's disease.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL04 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL05 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL02 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP04 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP05 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP02 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{\tiny{Mean time-slice accuracy} $\overline{C_{i,t}}$} & 100 &
			\multicolumn{2}{|r|}{\tiny{Mean accuracy} $\overline{C_{i}}$} & 100 \\
			\hline \hline

@@

\begin{table}
	\caption{Test results for experiment 2.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL08 & HC & 191 &  7  & 96.46 & 0.9646 & HC & 100 \\
			CTL12 & HC & 195 &  3  & 98.48 & 0.9848 & HC & 100 \\
			CTL01 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP08 & P   &  1  & 197 & 99.49 & 0.0050 &  P  & 100 \\
			ODP12 & P   &  2  & 196 & 98.99 & 0.0101 &  P  & 100 \\
			ODP01 & P   &  12  & 186 & 93.94 & 0.0606 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.90 &
			\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
			\hline \hline

@@

\begin{table}
\caption{Test results for experiment 3.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL03 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL13 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL14 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		ODP03 & P  &  53  & 145 & 73.23 & 0.2677 &  P  & 100 \\
		ODP13 & P  & 198 &   0   &     0    &      1      & HC  & 0 \\
		ODP14 & P  & 48  &  150 & 75.76  & 0.2424 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 74.83 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 83.33 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 4.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL12 & HC & 185 & 13  & 93.43 & 0.9343 & HC & 100 \\
		CTL06 & HC & 197 &  1   & 99.49 & 0.9949 & HC & 100 \\
		CTL11 & HC & 170 & 28  & 85.86 & 0.8586 & HC & 100 \\
		ODP12 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP11 & P  &   2   & 196 & 98.99 & 0.0101  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 96.30 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100  \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 5.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL15 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		CTL11 & HC & 198  &   0   &  100  & 1 & HC & 100 \\
		CTL07 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		ODP15 & P   &   0   & 198 &  100  & 0 &  P  & 100 \\
		ODP11 & P   &  34  &  164 &82.83& 0.1717 &  P  & 100 \\
		ODP07 & P  &   0   &  198 & 1 00  &0  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.14 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 6.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL10 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL03 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL02 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		ODP10 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP03 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP02 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 100 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 7.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL05 & HC & 194 &  4   & 97.98 & 0.9798 & HC & 100 \\
		CTL04 & HC & 198 &  0   &   100  &      1     & HC & 100 \\
		CTL10 & HC & 186  &  12 & 93.94 & 0.9394 & HC & 100 \\
		ODP05 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP04 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP10 & P  &   0    & 198 &   100  &    0      &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 98.65 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

@@

\begin{table}
\caption{Test results for experiment 8.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{i,hc}$ & $N_{i,p}$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL09 & HC & 102 & 96  & 51.51 &  0.5151 & HC  & 100 \\
		CTL12 & HC & 122 &  76  & 61.62 & 0.6162 & HC & 100 \\
		CTL06 & HC & 198 &   0  &  100   &    1       & HC & 100 \\
		ODP09 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\
		ODP12 &  P  &   2   & 196 & 98.99 & 0.0101 &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 85.35 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline
